Data Prep: IUCN and AquaMaps

### 2016-02-12 data_explore/data_prep.Rmd
got some code for finding occurrence info... let it run on Neptune!

``` {r get_counts, echo = FALSE}
x <- occ_search(scientificName = spp_iucn_marine$sciname[1:100], fields = 'minimal', limit = 25)
y <- sapply(x, function(x) x$meta$count)
```

>>>>

``` {r spp_all with observation counts}
spp_all <- read_csv(file.path(dir_data, 'spp_all.csv'))

library(rgbif)
# library(robis)

x <- occ_search(scientificName = spp_all$sciname[1:100], fields = 'minimal', limit = 5)
y <- sapply(x, function(x) x$meta$count)
z <- data.frame(sciname = names(y), obs = y)

z <- z %>% 
  left_join(spp_all %>%
              select(iucn_sid, am_sid, sciname),
            by = 'sciname') %>%
  left_join(read_csv(file.path(dir_data_remote, 'aquamaps/v2015/csv/speciesoccursum.csv')) %>%
                       select(am_sid = speciesid, occurcells),
                     by = 'am_sid') %>%
  mutate(ln_obs        = log(obs + 1),
         ln_occurcells = log(occurcells + 1))

plot(ln_obs ~ ln_occurcells, data = z)
